---
title: "Code along day 1"
author: "Julia Moeller"
date: "2023-09-06"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    toc_collapsed: true

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The following markdown has the correct code for the Code along section of Shiny training day 1.

# Empty Shiny app

```{r, eval = FALSE}
library(shiny)

ui <- fluidPage(
  ) # end fluidPage

server <- function(input, output){
}

shinyApp(ui = ui, server = server)

```

# App layout: Sidebar

```{r, eval = FALSE}
library(shiny)

ui <- fluidPage(
  
  titlePanel("This is a Shiny app"),
  
  sidebarLayout(
    sidebarPanel(
      "Sidebar",
      br(), 
      "Some other text in the sidebar"
      ), # end sidebarPanel
    
    mainPanel(
      "Main section",
      br(),
      br(),
      br(),
      "Some other text in the main section"
    ) # end mainPanel
    ) # end sidebarLayout
  ) # end fluidPage

server <- function(input, output){
}

shinyApp(ui = ui, server = server)
```

# NYC Dogs

## V1: Default data table
### UI
```{r, eval = FALSE}
library(shiny)
library(tidyverse)

nyc_dogs <- read_csv("data/nyc_dogs.csv")

ui <- fluidPage(
  
  radioButtons(inputId = 'gender',
               label = "Male or female dogs?",
               choices = c("Male", "Female")),
  
  tableOutput("table_output")
  
) # end fluidPage

```

### Server
```{r, eval = FALSE}
server <- function(input, output) {
  
  output$table_output <- renderTable({
    nyc_dogs %>%
      filter(gender == input$gender) %>%
      slice(1:10)
  })

}

# Run the application 
shinyApp(ui = ui, server = server)
```

## V2: DT data table
### UI
```{r, eval = FALSE}
library(shiny)
library(tidyverse)

nyc_dogs <- read_csv("data/nyc_dogs.csv")

ui <- fluidPage(
  
  radioButtons(inputId = 'gender',
               label = "Male or female dogs?",
               choices = c("Male", "Female")),
  
  DT::dataTableOutput("table_output")
  
) # end fluidPage

```

### Server
```{r, eval = FALSE}
server <- function(input, output) {
  
  output$table_output <- DT::renderDataTable({
    nyc_dogs %>%
      filter(gender == input$gender)
  })

}

# Run the application 
shinyApp(ui = ui, server = server)
```


## V3: Columns and filters

### UI
```{r, eval = FALSE}
library(shiny)
library(tidyverse)

nyc_dogs <- read_csv("data/nyc_dogs.csv")

ui <- fluidPage(
  
  fluidRow(
    column(3, 
           radioButtons(inputId = 'gender',
                        label = "Male or female dogs?",
                        choices = c("Male", "Female"))
           ), # end column
    column(3, 
           selectInput(inputId = "breed",
                       label = "Which breed?",
                       choices = unique(nyc_dogs$breed))
           ) # end column
    ), # end fluidRow
  
  tableOutput("table_output")
  
) # end fluidPage
```

### Server
```{r, eval = FALSE}
server <- function(input, output) {
  
  output$table_output <- renderTable({
    nyc_dogs %>%
      filter(gender == input$gender) %>%
      filter(breed == input$breed)
  })

}

# Run the application 
shinyApp(ui = ui, server = server)
```

## V3.1 Four filters gender, colour, breed, borough

### U1
```{r, eval = FALSE}
ui <- fluidPage(
  
  fluidRow(
    column(3, 
           radioButtons(inputId = 'gender',
                        label = "Male or female dogs?",
                        choices = c("Male", "Female"))
           ), # end column
    column(3, 
           selectInput(inputId = "colour",
                       label = "Which colour?",
                       choices = unique(nyc_dogs$colour))
           ), # end column
    column(3, 
           selectInput(inputId = "breed",
                       label = "Which breed?",
                       choices = unique(nyc_dogs$breed))
           ), # end column
    column(3, 
           selectInput(inputId = "borough",
                       label = "Which borough?",
                       choices = unique(nyc_dogs$borough))
           ), # end column
    ), # end fluidRow
  
  tableOutput("table_output")
  
) # end fluidPage
```

### Server
```{r, eval = FALSE}
server <- function(input, output) {
  
  output$table_output <- renderTable({
    nyc_dogs %>%
      filter(gender == input$gender) %>%
      filter(colour == input$colour) %>%
      filter(breed == input$breed) %>%
      filter(borough == input$borough)
  })

}

# Run the application 
shinyApp(ui = ui, server = server)
```

## V4: Plots

### UI
```{r, eval = FALSE}
library(shiny)
library(tidyverse)

nyc_dogs <- read_csv("data/nyc_dogs.csv")

ui <- fluidPage(
  
  fluidRow(
    column(6, 
           radioButtons(inputId = 'gender',
                        label = "Male or female dogs?",
                        choices = c("Male", "Female"))
           ), # end column
    column(6, 
           selectInput(inputId = "breed",
                       label = "Which breed?",
                       choices = unique(nyc_dogs$breed))
           ), # end column
    ), # end fluidRow
  
  fluidRow(
    column(6,
           plotOutput(outputId = "colour_barchart")
           ), # end column
    column(6,
           plotOutput(outputId = "borough_barchart")
    ), # end column
  ) # end fluidRow
) # end fluidPage
```

### Server (v1)
 
```{r, eval = FALSE}
server <- function(input, output) {
  
  filtered_data <- nyc_dogs %>%
    filter(gender == input$gender) %>%
    filter(breed == input$breed)
  
  output$colour_barchart <- renderPlot({
    ggplot(filtered_data) +
      geom_bar(aes(x = colour))
  }) 
  
  output$borough_barchart <- renderPlot({
    ggplot(filtered_data) +
      geom_bar(aes(x = borough))
  })

}
```

Error in Console.

### Server (v2)

```{r, eval = FALSE}
server <- function(input, output) {
  
  filtered_data <- reactive({
    nyc_dogs %>%
      filter(gender == input$gender) %>%
      filter(breed == input$breed)
  })
  
  output$colour_barchart <- renderPlot({
    ggplot(filtered_data()) +
      geom_bar(aes(x = colour))
  })
  
  output$borough_barchart <- renderPlot({
    ggplot(filtered_data()) +
      geom_bar(aes(x = borough))
  })

}

# Run the application 
shinyApp(ui = ui, server = server)
```

## V5: Multiple tabs

### Tab 1: Table
```{r, eval = FALSE}
ui <- fluidPage(
  
  titlePanel("NYC DOGS"),
  
  navbarPage("Navigation Bar",
             tabPanel(title = "Table",
                      fluidRow(
                        column(3, 
                               radioButtons(inputId = 'gender',
                                            label = "Male or female dogs?",
                                            choices = c("Male", "Female"))
                               ), # end column
                        column(3, 
                               selectInput(inputId = "colour",
                                           label = "Which colour?",
                                           choices = unique(nyc_dogs$colour))
                               ), # end column
                        column(3,
                               selectInput(inputId = "borough",
                                           label = "Which borough?",
                                           choices = unique(nyc_dogs$borough))
                               ), # end column
                        column(3,
                               selectInput(inputId = "breed",
                                           label = "Which breed?",
                                           choices = unique(nyc_dogs$breed))
                               ) # end column
                        ), # end fluidRow
                      
                      tableOutput("table_output")), # end tabPanel
  )
)
```

### Tab2 and 3: Plot and information

```{r, eval = FALSE}

ui <- fluidPage(
  
  titlePanel("NYC DOGS"),
  
  navbarPage("Navigation Bar",
             tabPanel(title = "Table",
                      fluidRow(
                        column(3, 
                               radioButtons(inputId = 'gender',
                                            label = "Male or female dogs?",
                                            choices = c("Male", "Female"))
                               ), # end column
                        column(3, 
                               selectInput(inputId = "colour",
                                           label = "Which colour?",
                                           choices = unique(nyc_dogs$colour))
                               ), # end column
                        column(3,
                               selectInput(inputId = "borough",
                                           label = "Which borough?",
                                           choices = unique(nyc_dogs$borough))
                               ), # end column
                        column(3,
                               selectInput(inputId = "breed",
                                           label = "Which breed?",
                                           choices = unique(nyc_dogs$breed))
                               ) # end column
                        ), # end fluidRow
                      
                      tableOutput("table_output")), # end tabPanel
             
             tabPanel(title = "Plot",
                      fluidRow(
                        column(6,
                               radioButtons(inputId = "gender_chart",
                                            label = tags$i("Male or Female Dogs?"),
                                            choices = c("Male", "Female"))
                        ), # end column
                        column(6,
                               selectInput(inputId = "breed_chart",
                                           label = tags$i("Which Breed?"),
                                           choices = unique(nyc_dogs$breed))
                        ) # end column
                      ), # end fluidRow
                      
                      fluidRow(
                        column(6,
                               plotOutput("colour_barchart")
                        ), # end column
                        column(6,
                               plotOutput("borough_barchart"))
                        ) # end fluidRow
                      ), # end tabPanel
             tabPanel(title = "Information",
                      p("This data has been taken from the NYC Department of health and", br(),
                        "shows the popularity of dog names in New York City by gender, colour,", br(),
                        "breed and borough."),
                      p(tags$a("The NYC Department of Health Website", 
                               href = "https://www.health.ny.gov/"))) # end of tabPanel
             ) # end navbarPage
  ) # end fluidPage

```

### Server

```{r, eval = FALSE}
server <- function(input, output) {
  
  table_data <- reactive({
    nyc_dogs %>%
      filter(gender == input$gender) %>%
      filter(breed ==  input$breed) %>%
      filter(colour ==  input$colour) %>%
      filter(borough ==  input$borough)
  })
  
  output$table_output <- renderTable({
    table_data()
  })
  
  plot_data <- reactive({
    nyc_dogs %>%
      filter(gender == input$gender_chart) %>%
      filter(breed ==  input$breed_chart)
  })
  
  output$colour_barchart <- renderPlot({
    ggplot(plot_data()) +
      geom_bar(aes(x = colour))
  })
  
  output$borough_barchart <- renderPlot({
    ggplot(plot_data()) +
      geom_bar(aes(x = borough))
  })

}

# Run the application 
shinyApp(ui = ui, server = server)
```

## Icons and themes

```{r, eval = FALSE}
ui <- fluidPage(
  
  theme = shinytheme("flatly"),
  
  titlePanel(tags$h1("NYC DOGS")),
  
  navbarPage("Navigation Bar",
             tabPanel(title = "Table",
                      icon = icon("table"),
                      fluidRow(
                        column(3, 
                               radioButtons(inputId = 'gender',
                                            label = "Male or female dogs?",
                                            choices = c("Male", "Female"))
                               ), # end column
                        column(3, 
                               selectInput(inputId = "colour",
                                           label = "Which colour?",
                                           choices = unique(nyc_dogs$colour))
                               ), # end column
                        column(3,
                               selectInput(inputId = "borough",
                                           label = "Which borough?",
                                           choices = unique(nyc_dogs$borough))
                               ), # end column
                        column(3,
                               selectInput(inputId = "breed",
                                           label = "Which breed?",
                                           choices = unique(nyc_dogs$breed))
                               ) # end column
                        ), # end fluidRow
                      
                      tableOutput("table_output")), # end tabPanel
             
             tabPanel(title = "Plot",
                      icon = icon("chart-area"),
                      fluidRow(
                        column(6,
                               radioButtons(inputId = "gender_chart",
                                            label = tags$i("Male or Female Dogs?"),
                                            choices = c("Male", "Female"))
                        ), # end column
                        column(6,
                               selectInput(inputId = "breed_chart",
                                           label = tags$i("Which Breed?"),
                                           choices = unique(nyc_dogs$breed))
                        ) # end column
                      ), # end fluidRow
                      
                      fluidRow(
                        column(6,
                               plotOutput("colour_barchart")
                        ), # end column
                        column(6,
                               plotOutput("borough_barchart"))
                        ) # end fluidRow
                      ), # end tabPanel
             tabPanel(title = "Information",
                      icon = icon("circle-info"),
                      p("This data has been taken from the NYC Department of health and", br(),
                        "shows the popularity of dog names in New York City by gender, colour,", br(),
                        "breed and borough."),
                      p(tags$a("The NYC Department of Health Website", 
                               href = "https://www.health.ny.gov/"))) # end of tabPanel
             ) # end navbarPage
  ) # end fluidPage
```

